Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-03 paper/paper.qmd
added future steps section in discussion part

## Weaknesses and next steps

>>>>

## Next Steps

To enhance the predictive power of the model, historical voting data, economic
indicators and major news events can be used as background variables. By analyzing
the impact of similar factors on voter sentiment in past elections, we can gain
insight into patterns and trends that may apply to the current campaign. For
example, high-profile events have historically influenced voter opinion, and
understanding these influences can provide a more complete picture of the factors
that drive support for each candidate. Given the underlying conditions that influence
voter preferences over time, this additional context would allow the model to make
more informed predictions.

Another possible improvement is the addition of detailed demographic information, such as age,
gender, income level, and educational background, which would allow us to identify trends among
specific groups of voters and thus greatly enhance our analysis. Different demographics often
have unique responses to campaign issues and activities; for example, younger voters may
prioritize different issues compared to older voters, and income level and educational
attainment may influence political preferences in complex ways. By incorporating this level
of granularity, future analyses can provide deeper insights into voter behavior and help
develop more targeted campaign strategies.
